\TOWRITE{ALL}{Proofread WP 5 Management pass 1}
\begin{draft}
\TOWRITE{PS (Work Package Lead)}{For WP leaders, please check the following (remove items
once completed)}
\begin{verbatim}
- [ ] have all the tasks in this Work Package a lead institution?
- [ ] have all deliverables in the WP a lead institution?
- [ ] do all tasks list all sites involved in them?
- [ ] does the table of sites and their PM efforts match lists of sites for each task?
      (each site from the table is listed in all relevant tasks, and no site is listed
      only in the table or only at some task)

- [ ] Binder / repo2docker documentation: tutorials and best practice guides -
      have we got this covered?
\end{verbatim}
\end{draft}
% (41)/36 = 1.138888 -> !1.14
\begin{workpackage}[id=education,wphases=0-36!0.97,
  title={Dissemination, education and engagement},
  short={Dissemination, education, and engagement},
  lead=IFR,
  IFRRM=10,
  MPRM=6,
  SRLRM=7,
  QSRM=3,
  UIORM=9,
  swsites
]


\begin{wpobjectives}
  A key focus of this work package is to disseminate the results of this
  project, including the technical advances and guidance for best practice for
  reproducible science. This includes educating researchers about the value of
  open science, reproducibility and re-usability as well as the possibilities of
  integrating Binder tools in their workflows.

  Beyond this activity, which is directed from the project members to the wider community of
  scientists, we use this work package to engage with researchers and
  stakeholders and seek input from them to the project. Desired input includes
  requirements for practical reproducibility in the different domain as well as
  technical contributions -- for example through merge requests for Binder
  tools, or open source documentation of best practice for reprocudible software
  environments.

  Our dissemination, education and engagement objectives includes:
 \begin{compactitem}
   \item Ensure awareness of the results of the project in the user community,
     and in particular in those groups that act as educators and multipliers of
     knowldege (such as the Carpentries and research infrastructure organisations).
   \item Educate the community on the value of open science, and in particular
   \item train researchers in best practices for open and reproducible science.
   \item Produce and training and education material to disseminate the ability to
     publish reproducible computational science outputs using the tools we
     improve and develop.
   \item Address the shortage of researchers and research support staff trained
     in practical reproducibility.
   \item Provide documentation and tutorials which can serve as the technical
     components of reproducibility policies.
   \item Throughout these activities engage with users and stakeholders, to
     listen and understand their barriers or incentives towards more
     reproducible science, and the usability of the \TheProject outputs.
 \end{compactitem}
\end{wpobjectives}

% Potential sources of inspiration: ODK's WP2 work package about dissemination:
% PDF: p.36 of https://github.com/OpenDreamKit/OpenDreamKit/raw/master/Proposal/proposal-www.pdf
% Sources: https://github.com/OpenDreamKit/OpenDreamKit/blob/master/Proposal/WorkPackages/DisseminationCommunityBuilding.tex

\begin{wpdescription}

  Open science and reproducible science is entirely dependent on researchers
  adopting open practices. In \TheProject, we improve and developing tools that
  can facilitate these practices, but they only work if researchers actually adopt
  them. For researchers to adopt the practices, they need to (i) know about them
  and (ii) want to use them.

  We address this challenge in multiple ways:
  \begin{enumerate}
  \item The philosophy of the Binder tools is to respect existing standards and
    best practice (and not to invent additional syntax or requirements). It is
    thus possible to use the Binder tools (to recreate a software environment)
    even if the repository authors did not anticipate the use of Binder, or knew
    about their existence. In the best possible scenario, a scientific research
    output becomes automatically reproducible with Binder without the
    \emph{author having to know about Binder or having to invest additional
      effort} (beyond following best practice).

    \item In this work package, we produce education materials and carry out
      education activities to spread the knowledge about \emph{good practice for
        reproducibility and re-usability in science}, such as for example
      automation of all analysis steps, and complete documentation of the
      required software stack. Only one aspect of this training is to show how
      Binder can help with reproducibility.

      Attendees and users following such training and advice will create more
      reproducible artifacts. If they -- or later users of their published
      artifacts -- want to use Binder to reproduce or re-use the results, they
      can. Even if they do not, we will have achieved an improvement of the
      reproducibility of scientific artifacts.

    \item Throughout the activities of this project and the engagement with the
      wider science community, we aim to understand the underlying drivers for
      acceptance, rejection or lack-of-interest in adopting practices that lead
      to reproducible science results.
  \end{enumerate}

  % HF: I think training the wider (non-scientist) public about Binder is going
  % too far?
  %
  % Going further, it is also clear that open science is not just of value
  % to researchers: one of the largest benefits of open science is that it makes
  % science accessible to the broader public who may not be members of the
  % research community.
  %
  % To this end, in addition to training researchers, we will also train the
  % public in how to make use of the open science research and services
  % facilitated by \TheProject. This will be done through regular open
  % dissemination and training workshops, as well as by producing and maintaining
  % material for online courses and documentation.

  The \TheProject project will develop, through \WPref{applications}, a number
  of demonstrator repositories that show examples of reproducibility in
  different scientific domains. (We use
  those activities to inform and evaluate the technical improvement to the
  Binder tools in \WPref{reproducibility} and \WPref{impact}). We also use those
  studies to create tutorials and \emph{best practice guides for
    reproducibility} (\localtaskref{online-resources}) in this work package, and
  offer interactive workshops (\localtaskref{workshops}) to help disseminate the
  content more effectively.

  As with all the code, test and build infrastructure produced as part of the
  project, we will also make all documentation open source. Our documentation --
  which includes best practice guides for reproducibility -- can thus be
  modified and improved after the end of the project to react to new
  developments (\delivref{education}{education-materials2}).

  We will engage with the scientific to support them in making their
  work more reproducible with Binder tools. The project will benefit from these interactions
  as we will learn more about reproducibility requirements and usefulness of the
  Binder tools, so that we can tailor our work to support scientific communities as broad as possible
  (\localtaskref{community-support}).

  We will also participate in the well established academic dissemination
  activities, and events of the European e-infrastructure projects and other
  relevant structures. EGI is a member of our the community engagement panel
  (\taskref{management}{community-engagement-panel}) and the interaction with
  them will be useful to prioritise our resources in this very active field.

  Open access to all publications resulting from the project will be ensured.
  %\TODO{Should this sentence go into a data / IPR management plan?}
\end{wpdescription}

\begin{tasklist}
\input{tasks/online-resources}
\input{tasks/training}
\input{tasks/community-support}
\end{tasklist}

\begin{wpdelivs}
  \begin{wpdeliv}[due=24,id=best-practice-guide,dissem=PU,miles=prototype,nature=R,lead=UIO]
  {Best practice guide for reproducible science with Binder.}
\end{wpdeliv}
\begin{wpdeliv}[due=36,id=education-materials2,dissem=PU,miles=final,nature=R,lead=UIO]
  {All training sessions material completed, reviewed, and published online.}
\end{wpdeliv}
% \begin{wpdeliv}[due=36,id=report2,dissem=PU,miles=final,nature=R,lead=UIO]
%   {Community building: Report on impact of development workshops, dissemination and training activities.}
% \end{wpdeliv}
\end{wpdelivs}

\end{workpackage}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../proposal"
%%% End:

%  LocalWords:  workpackage wphases wpobjectives wpdescription pageref wpdelivs wpdeliv
%  LocalWords:  dissem mailinglists swrepository final-mgt-rep compactitem swsites ipr
%  LocalWords:  TOWRITE tasklist delivref
