\section{Technical appendix}\label{sec:appendix}
\subsection{Terminology}\label{sec:terminology}

For clarity, we define some terms that have been used
throughout this proposal. We illustrate the terms in the context of the
reproducibility example in Section~\ref{sec:reproducibility-example}.

In particular, we imagine that we have a publication that contains
figure~\ref{fig:reproducibility-example-covid} as a result, and we want to
archive and make available \cite{ReproducibilityRepositoryExample2022} the
necessary information for others to reproduce that figure.

\begin{description}
\item[Repository] We refer to a \emph{repository} as a collection of files.

The \emph{purpose} of the repository in our context is to archive information to make
research results reproducible.

Such a repository could be a git repository (which could be hosted on GitHub,
Bitbucket, GitLab, or other services), but it could also just be a zip file of a
collection of files.

The repository could be made publicly available, for example through Zenodo,
Figshare, as an electronic supplementary to a publication, or through GitHub.

It is not unusual that a larger number of files might be
organised in subdirectories within the repository.

Our example repository\footnote{
  https://github.com/fangohr/reproducibility-repository-example/} \cite{ReproducibilityRepositoryExample2022} contains the following files:

\begin{description}
\item[\softwarename{README.md}]: an overview of the content of the repository
\item[\softwarename{figure1.ipynb}]: notebook that creates
  \softwarename{figure1.pdf} from
  the raw data. Could also be realised through a script or other executable
  program of some kind.
\item[\softwarename{requirements.txt}]: software specification
\item[\softwarename{time\_series\_covid19\_deaths\_global.csv}]: raw data
\end{description}

\item[Script] A machine-executable file (for example a Bash, Python, Perl
script, Makefile or similar). Such scripts can execute data processing commands,
and are often part of a repository to make the (automatic) reproduction of
results possible.

In our example, the necessary steps to create the figure from the raw data are
gathered in the notebook \texttt{figure1.ipynb}.

\item[Notebook] A Jupyter notebook. In short, an executable document that can
  combine text, code, and computation results. A Jupyter notebook can be used like a
  script. The notebook is explained in Section \fullref{sec:jupyter-notebook}.

\item[Software specification] The software specification depends on the software
  tools used. In our example, the \texttt{requirements.txt} file contains
\begin{verbatim}
pandas==1.3.4
matplotlib==3.4.3
\end{verbatim}
to indicate that we need the pandas and matplotlib package with the respective
versions 1.3.4 and 3.4.3.

\item[Software environment] All the software that needs to be available and
  installed to execute the scripts and (and if desired) Jupyter notebooks.

\item[Project Binder] The Project Binder is described in Section
\ref{seq:project-binder}. It is part of the Jupyter ecosystem of tools, and
allows to convert a repository with Jupyter notebooks into an browser-hosted
environment, in which the notebooks can be executed interactively (and thus
results can be reproduced).

\item[Binder tools] The Binder tools consist of \binderhub{}
  (Section~\ref{sec:binderhub}) and \repotodocker{} (see
  Section~\ref{sec:repo2docker}) .

\item[\repotodocker] \repotodocker{} is a tool that can automatically create a
\emph{software environment} (currently within a Docker container) in which the
notebooks and scripts of a repository can be executed
(Section~\ref{sec:repo2docker} and \ref{binder-how-does-it-work}).
\end{description}

\input{project-jupyter.tex}
\input{project-binder.tex}

% Not relevant here. Should remove that file later.
% \input{jupyter-services.tex}

