% \subsection{Context and motivation}


\begin{draft}

In many scientific disciplines, it is common for researchers to rely on
heterogeneous computational tools and technologies to collect data, explore the
input datasets, run simulations, visualise the outcome, and share their result
with peers or with a larger audience. Often, such data analysis cycles are
iteratively refined.

For simple datasets, processes may remain manageable. However, when dealing with
larger and more complex use cases, including big data from research facilities
or High Performance Computing resources, the complexity makes iteration cycles
slower for the researchers. A complex iteration cycle also makes research
results more difficult to reproduce. Results that cannot be reproduced make
research ineffective: they create barriers towards re-using the results in
future research work, a critical aspect of open science. This situation is
exacerbated by the current and accelerating increase of the amount of scientific
data being available, including the data becoming accessible through the
EOSC-Hub. But this growing availability of data also provides a massive
opportunity for open science.

Project Jupyter has developed as one piece of various solutions to the data
deluge, by enabling the construction of computational services accessible from
anywhere, any web-browser-enabled device, with access to any data. Jupyter-based
tools such as \href{https://mybinder.org}{Binder} and repo2docker show great
promise for enabling researchers to better perform \textbf{reproducible and open
  science}. Jupyter was recognised for its contribution to data analysis in
research with the prestigious 2017 \emph{ACM Software System Award}, of which
previous winners include TCP/IP, UNIX, and the World Wide Web. It is widely used
today in research, education, and industry. We will build on these tools, both
improving their capabilities and expanding their accessibility to new
communities, both academic and demographic, in order to \textbf{further the
  mission of open science}.

In this proposal, core team members of Jupyter projects -- including
recipients of the \emph{ACM Software System Award} -- and key contributors to
the open source scientific computing ecosystem, detail improvements to the
capabilities of Project Jupyter-related tools to \textbf{facilitate reproducible science}.
By collaborating with a wide variety
of stakeholders from diverse scientific and educational domains, we aim to
demonstrate and ensure that such innovative open source tools -- built on Project
Jupyter -- are feasible, valuable, and effective in furthering reproducible and open science. The
goal is to \textbf{improve the accessibility, interactivity,
  reproducibility, and re-usability of computational research and open science.}

\end{draft}

\draftpage

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proposal"
%%% End:
