% template for a task
% each task should be added to exactly one workpackage
% in the workpackage task list
\begin{task}[
  title=Reducing technical constraints to enable broader usage,
  % task id for references
  id=constraints,
  % lead institution ID
  lead=SRL,
  PM=14,
  wphases={0-36},
  % partner institution ID(s)
  % don't include lead here
  partners={MP,QS}
]

In this task, we refactor and extend the existing code to be more flexible. In
particular, we want to address and remove the constraints that currently exist:

\begin{compactitem}
\item Dependency of existing Kubernetes system: at the moment, BinderHub can
  only start container environments within a Kubernetes installation. In this
  task, we will make it possible to start a container directly on the host
  machine. Setting up Kubernetis system is a complex task: while justified to
  exploit large computational resources through swarms of containers
  effectively, it is not necessary for single-machine execution of
  Binder-reproduced environments (such as anticipated for Binder@home in
  \taskref{applications}{binder-at-home}).
\item Support of only Docker containers to host created software environments.
  Docker is widespread and popular, and in particular has an attractive user
  interface for Windows and OSX. However, many HPC centres refuse to allow use
  of Docker containers on their systems for security reasons. In this task, we
  will make it possible to user container technologies, which are more
  acceptable to use on large HPC installations (such as singularity for
  example).
     % deliverable will be defined in the appropriate WorkPackage.tex
    % (\localdelivref{deliv-id})
  \end{compactitem}

  These steps are essential to enable the Binder@home
  (\taskref{applications}{binder-at-home}) and the Binder@HPC
  (\taskref{applications}{binder-at-hpc}) use cases.

%   The task includes the following activities
%   \begin{compactitem}
%   \item ...
%      % deliverable will be defined in the appropriate WorkPackage.tex
%     % (\localdelivref{deliv-id})
%   \end{compactitem}
\end{task}
